Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-10-13 paper/paperv3.qmd
Fixing lmer -> glmer

```{r}
#| label: setup
#| include: false  
library(ggthemes)
library(cowplot)
library(lme4)
library(lmerTest) # Loading this library will automatically append p-values to lmer models estimated using something called Satterthwaite's method
library(merTools)
library(tidyverse)
library(ggeffects)
library(ggridges)
library(patchwork)
> library(qpcR)
source(here::here("R/format.R"))
theme_set(theme_few(base_size = 13))

@@

detection_mod_line <- lmer(
  observed ~ age10 + (1 | year_fct) + (1 | animalID), 
  detection_seals
)

@@

breed_age_line <- lmer(
  observed_int ~ age10 + (1 | animalID) + (1 | year),
  sealdat
)

>>>>

```{r}
#| label: setup
#| include: false  
library(ggthemes)
library(cowplot)
library(lme4)
library(lmerTest) # Loading this library will automatically append p-values to lmer models estimated using something called Satterthwaite's method
library(merTools)
library(tidyverse)
library(ggeffects)
library(ggridges)
library(patchwork)
library(qpcR)
source(here::here("R/format.R"))
theme_set(theme_few(base_size = 13))

@@

detection_mod_line <- glmer(
  observed ~ age10 + (1 | year_fct) + (1 | animalID), 
  detection_seals, 
  family = "binomial"
)

@@

breed_age_line <- glmer(
  observed_int ~ age10 + (1 | animalID) + (1 | year),
  sealdat, 
  family = "binomial", 
  control = glmerControl(optimizer = "bobyqa")
)
